---
title: My dynamic report
output: html_fragment
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE, error=FALSE)
library(tidyverse)

```

```{css}
@import url('https://fonts.googleapis.com/css2?family=Bebas+Neue&family=Press+Start+2P&display=swap');

body{
background-color: #000000;
opacity: 0;
animation-name: fadeIn;
animation-duration: 2s;
animation-timing-function: ease-in;  
animation-fill-mode: forwards;
color: #ffffff

}

ul {
  display: inline-block;
  text-align: left;
  margin: 0 auto;
}

.intro {
max-width: 1000px;
margin: 1.5rem auto;
padding: 1.2rem 1.5rem;
border-radius: 14px;
line-height: 1.7;
text-align: left;

}


#observing-patterns-in-my-youtube-shorts-feed img {
  max-width: 100%;
  border-radius: 12px;
  display: block;
  margin: 1rem auto;
  display: flex;
  flex-direction: column;
  box-shadow: 0 4px 12px rgba(0,0,0,0.2);
  
}


p{
color: #ffffff;
font-size: 15px;



}
@keyframes fadeIn {
0% {opacity: 0;}
100% {opacity: 1;}
}

h1, h2{
font-family: "Press Start 2P";
font-weight: 400;
font-style: normal;
color: #2bb597;

}

h2{
font-size: 25px;

}

```

## Observing patterns in my Youtube Shorts feed

<div class = "intro">

This report tracks the Youtube shorts that appeared on my feed overtime. 
Each row in this dataset represents one observed short. This data includes numeric variables such as the length of the short and the likelyhood I would watch the creator again. I also have categorical variables such as the content category, AI voice usage and whether or not the creator's face is visible. </div>

```{r}

logged_data <- read_csv(
  "https://docs.google.com/spreadsheets/d/e/2PACX-1vSsLYiBG-Z4SvZwNfP-h2ET2zyMOv97CtmxCt-sL9JdrhAK6YQ1NuA8sZbo9Pt4_80zQ6Fs1GvOpGGn/pub?output=csv"
)

latest_data <- logged_data %>%
  rename(
    timestamp = 1,
    short_length = 2,
    face_visible = 3,
    category = 4,
    ai_voice = 5,
    watched_twice = 6,
    seen_creator_before = 7,
    watch_creator_again = 8
  )

category_data <- latest_data %>%
  separate_rows(category, sep = ",\\s*")

num_shorts <- latest_data$short_length %>%
  length()

mean_length <- latest_data$short_length %>%
  mean(na.rm = TRUE) %>%
  round(1)

mean_watch_again <- latest_data$watch_creator_again %>%
  mean(na.rm = TRUE) %>%
  round(1)

max_length <- latest_data$short_length %>%
  max(na.rm = TRUE)

category_data %>%
  ggplot() +
  geom_bar(aes(y = category)) +
  labs(
    title = "Categories of observed YouTube Shorts",
    x = "Count",
    y = "Category"
  )

latest_data %>%
  ggplot() +
  geom_bar(aes(x = ai_voice)) +
  labs(
    title = "Use of AI voice in observed YouTube Shorts",
    x = "AI voice",
    y = "Count"
  )


latest_data %>%
  group_by(ai_voice) %>%
  summarise(
    mean_watch_again = mean(watch_creator_again, na.rm = TRUE)
  ) %>%
  ggplot() +
  geom_col(aes(x = ai_voice, y = mean_watch_again)) +
  labs(
    title = "Average watch-again rating by AI voice use",
    x = "AI voice",
    y = "Mean watch-again rating"
  )

```

I recorded several pieces of information while analysing the data.

- I observed `r num_shorts` YouTube Shorts in total.
- The average length of the Shorts I watched was `r mean_length` seconds, with `r max_length` seconds being the longest length recorded.
- The average time I was likely to watch this creator again was `r mean_watch_again` out of 5

The last graph shows the likelyhood I would watch the creator again if there was an AI voice. 





